Excuse me, do you have a moment to talk about version control?

### 2017-10-05 README.Rmd
Delete "yes"

Git has been re-purposed by the data science community [@Ram2013;
@git-for-humans; @ten-simple-rules-git]. We use it to manage the motley collection of files that make up typical data analytical projects, which consist of data, figures, reports, and, yes, source code. Even those who identify more as statistician than data scientist generally have a similar mix of files that are the artifacts of a project.

>>>>

Git has been re-purposed by the data science community [@Ram2013;
@git-for-humans; @ten-simple-rules-git]. We use it to manage the motley collection of files that make up typical data analytical projects, which consist of data, figures, reports, and source code. Even those who identify more as statistician than data scientist generally have a similar mix of files that are the artifacts of a project.
